---
title: "HW 01 - Airbnb listings in NYC"
author: "Insert your name here"
date: "Insert date here"
output: github_document
---

## Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
nycbnb = read_csv("https://urmc-bst.github.io/bst430-fall2021-site/hw_lab_instruction/hw-01-airbnb/data/nylistings.csv")
```

## Exercises

### Exercise 1

Remove this text, and add your answer for Exercise 1 here.

### Exercise 2

Remove this text, and add your answer for Exercise 2 here.

### Exercise 3

Remove this text, and add your answer for Exercise 3 here.

```{r prices-neighbourhoods}
# remove this comment and add the code for Exercise 3 here
```

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

```{r top-5-median}
# remove this comment and add the code for Exercise 4 here
```

```{r top-5-median-plot}
# remove this comment and add the code for Exercise 4 here
```

```{r top-5-median-summary-stats}
# remove this comment and add the code for Exercise 4 here
```

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

```{r review-scores-rating}
# remove this comment and add the code for Exercise 5 here
```

### Exercise 6

```{r score-vs-price}
# remove this comment and add code for Ex 6
```

### Exercise 7

Remove this text and add your answer for Ex 7

### Exercise 8 (**extra credit**)

Remove this text and add your answer for Ex 8

```{r}
#remove this comment and add code for Ex 8
```

