---
title: "HW 01 - Airbnb listings in NYC"
author: "Jonathan Klus"
date: "4 September 2021"
output: github_document
---

## Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
nycbnb = read_csv("https://urmc-bst.github.io/bst430-fall2021-site/hw_lab_instruction/hw-01-airbnb/data/nylistings.csv")
```

## Exercises

### Exercise 1


*How many observations (rows) does the dataset have? Instead of hard coding the number in your answer, use inline code.*

```{r}
nrow(nycbnb)
```

The data set has `r nrow(nycbnb)` observations. 

### Exercise 2

*Run `View(nycbnb)` in your Console to view the data in the data viewer. What does each row in the dataset represent?*

Each row represents a single Airbnb property in New York City. 

### Exercise 3

*Create a faceted histogram where each facet represents a neighborhood and displays the distribution of Airbnb prices in that neighborhood. Think critically about whether it makes more sense to stack the facets on top of each other in a column, lay them out in a row, or wrap them around. Along with your visualisation, include your reasoning for the layout you chose for your facets.*

```{r prices-neighbourhoods}
ggplot(data = nycbnb, mapping = aes(x = price)) +
  geom_histogram(binwidth = 10) +
  facet_wrap(~ neighborhood) +  # or facet_grid...
  theme(strip.text.x = element_text(size=5))
```

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

```{r top-5-median}
# remove this comment and add the code for Exercise 4 here
```

```{r top-5-median-plot}
# remove this comment and add the code for Exercise 4 here
```

```{r top-5-median-summary-stats}
# remove this comment and add the code for Exercise 4 here
```

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

```{r review-scores-rating}
# remove this comment and add the code for Exercise 5 here
```

### Exercise 6

```{r score-vs-price}
# remove this comment and add code for Ex 6
```

### Exercise 7

Remove this text and add your answer for Ex 7

### Exercise 8 (**extra credit**)

Remove this text and add your answer for Ex 8

```{r}
#remove this comment and add code for Ex 8
```

